Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2019-11-03 PaperMagneticProfiles_JBSMSE.tex
Implement minor fixes.

\nomenclature[aq]{$\rate{q}\ped{csg}$}{volumetric casing losses in the AMR model [\si{\watt\per\cubic\meter}]}
\nomenclature[ic]{csg}{regenerator casing}
\nomenclature[ah]{$\hheat$}{heat transfer coefficient [\si{\watt\per\meter\squared\per\kelvin}]}
\nomenclature[aa]{$A\ped{sf}$}{contact surface area between solid and fluid phases in the regenerator [\si{\meter^2}]}
\nomenclature[is]{sf}{relative to the heat transfer between solid and fluid phases in the regenerator}
\nomenclature[bb]{$\beta$}{surface area density [\si{\squared\meter\per\cubic\meter}]}
\nomenclature[ak]{$k\ap{eff}$}{effective thermal conductivity [\si{\watt\per\meter\per\kelvin}]}
\nomenclature[ad]{$D\ped{ld}$}{dispersion term in the AMR model [\si{\meter\square\per\second}]}
\nomenclature[af]{$f$}{cycle frequency [\si{\hertz}]}
\nomenclature[bf]{$\Phi$}{utilization}
\nomenclature[am]{$m$}{mass [\si{\kg}]}

@@

@@

Figure~\ref{fig:cos_ins} shows the cooling capacity attained by the device at a frequency of \SI{1}{\hertz} and different utilizations. The horizontal axis shows the average field value during the high field region. The instantaneous profile almost always yields a higher performance, and since the average field during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels. For the ``same minimum'' comparison, the instantaneous profile is capable of keeping a low magnetic field over the entire half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.  As demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss.

>>>>

\nomenclature[aq]{$\rate{q}\ped{csg}$}{volumetric casing losses in the AMR model [\si{\watt\per\cubic\meter}]}
\nomenclature[ic]{csg}{regenerator casing}
\nomenclature[ah]{$\hheat$}{heat transfer coefficient [\si{\watt\per\meter\squared\per\kelvin}]}
\nomenclature[aa]{$A\ped{sf}$}{contact surface area between solid and fluid phases in the regenerator [\si{\meter^2}]}
\nomenclature[is]{sf}{relative to the heat transfer between solid and fluid phases in the regenerator}
\nomenclature[bb]{$\beta$}{surface area density [\si{\squared\meter\per\cubic\meter}]}
\nomenclature[ak]{$k\ap{eff}$}{effective thermal conductivity [\si{\watt\per\meter\per\kelvin}]}
\nomenclature[ad]{$D\ped{ld}$}{dispersion term in the AMR model [\si{\meter\square\per\second}]}
\nomenclature[af]{$f$}{cycle frequency [\si{\hertz}]}
\nomenclature[am]{$m$}{mass [\si{\kg}]}

@@

\nomenclature[ad]{$D\ped{p}$}{particle diameter [\si{meter}]}

@@

Figure~\ref{fig:cos_ins} shows the cooling capacity attained by the device at a frequency of \SI{1}{\hertz} and different utilizations. The horizontal axis shows the average field value during the high field region. The instantaneous profile almost always yields a higher performance, and since the average field during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels. In this comparison, the instantaneous profile is capable of keeping a low magnetic field over the entire half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.  As demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss.
